### 2019-07-22 monograph/thesis/chapters/beautifiers.tex
Removed unrelated references from beautifiers.tex
Created the list of interests with beautifiers.tex articles

\section{Application Fields}

\url{https://github.com/r-lib/styler}
\url{https://github.com/github/linguist}
\url{https://forum.sublimetext.com/t/auto-align-symbolic/34375}
\url{https://github.com/Thom1729/SmartIndent}
\url{https://github.com/wbond/package_control_channel/issues/4310} Write a formatter utility
\url{https://github.com/PyCQA/pydocstyle}
\url{https://github.com/PyCQA/pycodestyle}

\citeonline{annotationAssistant},
\citeonline{codePlagiarismDetection},
\citeonline{softwarePortfolio},
\citeonline{legacyAssets},
\citeonline{massMaintenance},
\citeonline{prettyPrinting},
\citeonline{architectureFormatting},
\citeonline{independentFramework},
\citeonline{industrialApplication},
\citeonline{toolsForProjectManagement},
\citeonline{codeClassification},
\citeonline{codeScanningPatterns},
\citeonline{debuggingIntoExamples},
\citeonline{programUnderstanding},
\citeonline{documentingAndSharingKnowledge},
\citeonline{autofoldingForSourceCode},
\citeonline{learningSupportSystem},
\citeonline{syntaxHighlightingInfluencing},
\citeonline{improvingCodeReadability},
\citeonline{howNovicesRead},
\citeonline{theRoleOfMethodChains},
\citeonline{codeComprehensionComparedToOO},
\citeonline{enhancingLegacySoftwareSystemAnalysis},
\citeonline{moldableCodeEditor},
\citeonline{blindAndSightedProgrammers},
\citeonline{pushdownAutomata},

\section{Continuous Integration}

On a distributed version control system,
continuous integration would be continuously running the system tests as long new code is integrated into main system from the distributed clients \cite{continuousIntegration}.

\begin{enumerate}[leftmargin=*]
    \item \citeonline{trackingChanges},
    \item \footnote{\url{https://blog.codinghorror.com/check-in-early-check-in-often/}}
    \item \cite{aspectOriented}
\end{enumerate}

\section{Language Server Protocol}

\url{https://www.youtube.com/watch?v=2GqpdfIAhz8}
\url{http://langserver.org/}
\url{https://github.com/Microsoft/language-server-protocol}
\url{https://github.com/SublimeCodeIntel/SublimeCodeIntel}
\url{https://code.visualstudio.com/blogs/2016/06/27/common-language-protocol}
\url{https://www.eclipse.org/community/eclipse_newsletter/2017/may/article1.php}
\url{https://github.com/Microsoft/language-server-protocol/wiki/Protocol-Implementations}

>>>>

\advisor{}{%
\section{Lista de curiosidades}

\lang{%
    On a distributed version control system,
    continuous integration would be continuously running the system tests as long new code is integrated into main system from the distributed clients \cite{continuousIntegration}.
}{}

\begin{enumerate}
    \item \citetitle{trackingChanges}
    \item \citetitle{aspectOriented}
    \item \citetitle{annotationAssistant}
    \item \citetitle{codePlagiarismDetection}
    \item \citetitle{softwarePortfolio}
    \item \citetitle{legacyAssets}
    \item \citetitle{massMaintenance}
    \item \citetitle{prettyPrinting}
    \item \citetitle{architectureFormatting}
    \item \citetitle{independentFramework}
    \item \citetitle{industrialApplication}
    \item \citetitle{toolsForProjectManagement}
    \item \citetitle{codeClassification}
    \item \citetitle{codeScanningPatterns}
    \item \citetitle{debuggingIntoExamples}
    \item \citetitle{programUnderstanding}
    \item \citetitle{documentingAndSharingKnowledge}
    \item \citetitle{autofoldingForSourceCode}
    \item \citetitle{learningSupportSystem}
    \item \citetitle{syntaxHighlightingInfluencing}
    \item \citetitle{improvingCodeReadability}
    \item \citetitle{howNovicesRead}
    \item \citetitle{theRoleOfMethodChains}
    \item \citetitle{codeComprehensionComparedToOO}
    \item \citetitle{enhancingLegacySoftwareSystemAnalysis}
    \item \citetitle{moldableCodeEditor}
    \item \citetitle{blindAndSightedProgrammers}
    \item \citetitle{pushdownAutomata}
    \item \url{https://github.com/r-lib/styler}
    \item \url{https://github.com/github/linguist}
    \item \url{https://github.com/wbond/package_control_channel/issues/4310} Write a formatter utility
    \item \url{https://github.com/PyCQA/pydocstyle}
    \item \url{https://github.com/PyCQA/pycodestyle}
    \item \url{https://blog.codinghorror.com/check-in-early-check-in-often/}
    \item \url{https://www.youtube.com/watch?v=2GqpdfIAhz8}
    \item \url{http://langserver.org/}
    \item \url{https://github.com/Microsoft/language-server-protocol}
    \item \url{https://github.com/SublimeCodeIntel/SublimeCodeIntel}
    \item \url{https://code.visualstudio.com/blogs/2016/06/27/common-language-protocol}
    \item \url{https://www.eclipse.org/community/eclipse_newsletter/2017/may/article1.php}
    \item \url{https://github.com/Microsoft/language-server-protocol/wiki/Protocol-Implementations}
\end{enumerate}
}
